Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-03-01 ForegroundSimulations/ms.tex
Update figures
From e0b14ff (master):
=====================

(*) Add and update figures

In ms.tex,

(*) Update figures

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{asm_foreground_eor_beam_chromaticity_fullband.eps}
\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra for different baselines.}
\label{fig:asm-dps-beam-chromaticity-baselines}
\end{figure*}

@@

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_150.0_MHz_subband.eps}
\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 150~MHz subband for different baseline lengths.}
\label{fig:asm-dps-beam-chromaticity-baselines-150-subband}
\end{figure*}

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband.eps}
\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 170~MHz subband for different baseline lengths.}
\label{fig:asm-dps-beam-chromaticity-baselines-170-subband}
\end{figure*}

@@

>>>>

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{asm_foreground_eor_beam_chromaticity_fullband_bhw2.0.eps}
\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra for different baselines.}
\label{fig:asm-dps-beam-chromaticity-baselines}
\end{figure*}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{spec_on_achrmbeam_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
\caption{Attenuation of foreground power (in dB) from antenna-to-antenna reflections required to keep the reflected foreground power below EoR H{\sc i} signal power.}
\label{fig:fg-reflections-achrmbeam}
\end{figure}

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_150.0_MHz_subband_win_method_bhw2.0.eps}
\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 150~MHz subband for different baseline lengths.}
\label{fig:asm-dps-beam-chromaticity-baselines-150-subband}
\end{figure*}

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband_win_method_bhw2.0.eps}
\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 170~MHz subband for different baseline lengths.}
\label{fig:asm-dps-beam-chromaticity-baselines-170-subband}
\end{figure*}

@@

\begin{figure*}[htb]
\centering
\subfloat[][Power patterns]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_150.0_MHz_subband.eps}}
\subfloat[][Power patterns]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_150.0_MHz_subband.eps}} \\
\subfloat[][Power patterns]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_170.0_MHz_subband.eps}}
\subfloat[][Power patterns]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
\caption{}
\label{fig:eor-fg-ratios}
\end{figure*}
